KidsAIR: Main analysis

### 2020-11-16 main_analysis_initial.Rmd
small analysis updates new analysis for interaction terms

count_summary <- kids_analysis_data_1obs_per_child %>% 
  #group_by(treatment) %>% # Change treatment grouping as necessary 
  #filter(lrti_incidence < 0.7) %>% 
  summarize(mean_events = mean(lrti_events, na.rm = TRUE),
            sd_events = sd(lrti_events, na.rm = TRUE),
            n_events = n(),
            min_events = min(lrti_events, na.rm = TRUE),
            median_events = median(lrti_events, na.rm = TRUE),
            max_events = max(lrti_events, na.rm = TRUE))
count_summary

@@

events_plot <- analysis_data %>% 
  ggplot() +
    geom_histogram(aes(lrti_events)) +
    theme_light() +
    facet_wrap(~treatment)
events_plot

@@

# Simple model with offset
nb_results <- glm.nb(lrti_events ~ treatment + offset(log_person_time_at_risk), 
                     data = analysis_data)

@@

poisson_results <- glm(lrti_events ~ treatment + offset(log_person_time_at_risk), 
                       family = "poisson", data = analysis_data)

>>>>

count_summary <- analysis_data %>% 
  #group_by(treatment) %>% # Change treatment grouping as necessary 
  #filter(lrti_incidence < 0.7) %>% 
  summarize(mean_events = mean(lrti_events_total, na.rm = TRUE),
            sd_events = sd(lrti_events_total, na.rm = TRUE),
            n_events = n(),
            min_events = min(lrti_events_total, na.rm = TRUE),
            median_events = median(lrti_events_total, na.rm = TRUE),
            max_events = max(lrti_events_total, na.rm = TRUE))
count_summary

@@

events_plot <- analysis_data %>% 
  ggplot() +
    geom_histogram(aes(lrti_events_total)) +
    theme_light() +
    facet_wrap(~treatment)
events_plot

@@

# Simple model with offset
nb_results <- glm.nb(lrti_events_total ~ treatment + offset(log_person_time_at_risk), 
                     data = analysis_data)

@@

poisson_results <- glm(lrti_events_total ~ treatment + offset(log_person_time_at_risk), 
                       family = "poisson", data = analysis_data)

### 2020-11-16 main_analysis_secondary_models.Rmd
small analysis updates new analysis for interaction terms

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 12 Nov 2020"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
library(DHARMa)
```

@@

itt_res <- simulateResiduals(itt_results)
plot(itt_res, rank = FALSE, quantreg = TRUE)
```

@@

@@

## Diagnostic plots
```{r}
plot(itt_pm_results, main = "PM ITT Primary model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_pm_results), main = "PM ITT Primary model")
qqline(residuals(itt_pm_results))

@@

@@

summary(logreg_results)

at_risk_summary <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize(mean(person_time_at_risk, na.rm = TRUE),
            sd(person_time_at_risk, na.rm = TRUE),
            median(person_time_at_risk, na.rm = TRUE))
at_risk_summary
```

>>>>

---
title: 'KidsAIR: Main analysis'
author: "Ethan Walker"
date: "Updated 13 Nov 2020"
output: pdf_document
---

@@

```{r}
library(readxl)
library(naniar)
library(lubridate)
library(emmeans)
library(broom)
library(broom.mixed)
library(zoo)
library(lme4)
library(lmerTest)
library(mctest)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MASS)
library(faraway)
library(DHARMa)
```

@@

itt_res <- simulateResiduals(itt_results)
plot(itt_res, rank = FALSE, quantreg = TRUE)

plot(itt_results, main = "ITT Primary model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_results), main = "ITT Primary model")
qqline(residuals(itt_results))
```

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try child_age, gender, home_floors_2level, home_sqft_2level

# Run primary model and print results
itt_results_int <- glmer.nb(lrti_events_total ~ treatment_assigned*child_age + 
#                                  child_age +
                        (1 | home:cohort:area) + 
                        offset(log_person_time_at_risk), data = analysis_data)
#write_rds(itt_results_int, paste0(file_path, "Output/itt_results_int_age.rds"))

summary(itt_results_int)

int_emmeans <- emmeans(itt_results_int, pairwise ~ treatment_assigned | child_age)
summary(int_emmeans, conf.int = TRUE)
confint(int_emmeans)
# This line will plot the interaction term
#emmip(itt_results_int, child_age ~ treatment_assigned, cov.reduce = range)
table(model.frame(itt_results_int)$treatment_assigned)
nobs(itt_results_int)
```

@@

## Diagnostic plots
### The correlation in the residuals vs fitted plot is due to the random term for "home"
```{r}
plot(itt_pm_results, main = "PM ITT Primary model", 
     xlab = "fitted values", ylab = "residuals")
qqnorm(residuals(itt_pm_results), main = "PM ITT Primary model")
qqline(residuals(itt_pm_results))

@@

```{r, eval=FALSE, include=FALSE}
# Effect modification/interaction analysis
# Try child_age, gender, home_floors_2level, home_sqft_2level

# Run primary model and print results
itt_pm_results_int <- glmer(log(pm_mean_sampling_period) ~ treatment_assigned*home_sqft_2level + 
                              child_age + 
                       (1 | home:cohort:area), data = analysis_data)
#write_rds(itt_pm_results_int, paste0(file_path, "Output/itt_pm_results_int_age.rds"))

summary(itt_pm_results_int)

int_emtrends <- emtrends(itt_pm_results_int, home_sqft_2level ~ treatment_assigned, var = "log(pm_mean_sampling_period)")
summary(int_emtrends, conf.int = TRUE)
# This line will plot the interaction term
#emmip(itt_pm_results_int, child_age ~ treatment_assigned, cov.reduce = range)
table(model.frame(itt_pm_results_int)$treatment_assigned)
nobs(itt_pm_results_int)
```

@@

summary(logreg_results)
```

## At-risk period across treatment arms
```{r}
at_risk_summary <- analysis_data %>% 
  group_by(treatment_assigned) %>% 
  summarize("Mean at-risk time" = mean(person_time_at_risk, na.rm = TRUE),
            "SD at-risk time" = sd(person_time_at_risk, na.rm = TRUE),
            "Med at-risk time" = median(person_time_at_risk, na.rm = TRUE))
at_risk_summary
```
